Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-17 _03_smoothing_tracks.Rmd
edits to smoothing values
edit thinning figure

We apply a median smooth with four different values of $K$, the moving window size --- 3, 5, 11, and 21 positions.
$K$ must be an odd number, but apart from that there is no correct magnitude of $K$.
Very large $K$ will lead to unrealistic tracks, while small $K$ will not result in much reduction of error.
Users are encouraged to plot their data before and after smoothing to examine the effect of different window sizes.

@@

![](figures/fig_04_median_smooth.png)

@@

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg) +
  geom_hline(
    yintercept =
      1 + quantile(data$speed,
        na.rm = T,
        probs = c(0.5, 0.95)
      ),
    lty = c(1, 2)
  ) +
  geom_boxplot(
    data = speed_agg_smooth,
    aes(
      x = as.factor(interval),
      y = 1 + speed
    ),
    fill = pal[3],
    show.legend = F,
    width = 0.25,
    outlier.size = 0.2,
    position = position_nudge(x = 0.25)
  ) +
  geom_boxplot(aes(factor(interval), 1 + speed),
    position = position_nudge(x = -0.25, ),
    fill = "grey",
    alpha = 0.5,
    show.legend = F,
    width = 0.25,
    outlier.size = 0.2
  ) +
  scale_y_log10(
    label = scales::comma,
    limits = c(NA, 1.005)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    x = "Interval (s)",
    y = "Speed"
  )
```

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(
    fig_agg_data_smooth, fig_agg_data_error, fig_agg_speed,
    design = "AABBC"
  ) +
    plot_annotation(
      tag_levels = "a",
      tag_prefix = "(",
      tag_suffix = ")"
    ) &
    theme(plot.tag = element_text(face = "bold"))

>>>>

We apply a median smooth with four different values of $K$, the moving window size --- 5, 11, 21 and 101 positions.
$K$ must be an odd number, but apart from that there is no correct magnitude of $K$.
Very large $K$ will lead to unrealistic tracks, while small $K$ will not result in much reduction of error.
Users are encouraged to plot their data before and after smoothing to examine the effect of different window sizes.

@@

@@

```{r echo=FALSE}
# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg) +
  geom_hline(
    yintercept =
      1 + quantile(data$speed,
        na.rm = T,
        probs = c(0.5, 0.95)
      ),
    lty = c(1, 2)
  ) +
  geom_boxplot(
    data = speed_agg_smooth,
    aes(
      x = as.factor(interval),
      y = 1 + speed
    ),
    fill = pal[3],
    size = 0.3,
    show.legend = F,
    width = 0.25,
    outlier.size = 0.2,
    position = position_nudge(x = 0.15)
  ) +
  geom_boxplot(aes(factor(interval), 1 + speed),
    position = position_nudge(x = -0.15, ),
    fill = "grey",
    size = 0.3,
    alpha = 0.5,
    show.legend = F,
    width = 0.25,
    outlier.size = 0.2
  ) +
  scale_y_log10(
    label = scales::comma,
    limits = c(NA, 1.005)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text.y = element_blank()
  ) +
  labs(
    x = "Interval (s)",
    y = "Speed"
  )
```

```{r echo=FALSE}
# make combined figure
fig_aggregate <-
  wrap_plots(
    fig_agg_data_smooth, fig_agg_data_error, fig_agg_speed,
    design = "AABBCC"
  ) +
    plot_annotation(
      tag_levels = "a",
      tag_prefix = "(",
      tag_suffix = ")"
    ) &
    theme(plot.tag = element_text(face = "bold"))
